Raw Traces

### 2023-05-19 Fish Data Analysis/Raw Traces Figure.qmd
Finalizing plots before reorganization

This is to make sure that it's the smae size after I do supsmu
```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

@@

@@

nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance < 2 | all_nas) %>%
                                    mutate(row_n = row_number(),
                                           remove = ifelse(row_n > 1 & is.na(Distance),"Y","N")) %>%
                                    filter(remove == "N") %>%
                                    ungroup() %>%
                                    filter(Frame_Num %in% c(10)) %>% 
                                    mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
                                    select(c(Frame_Num, Fish1, Fish2, Grouping)) %>%
                                    pivot_longer(c(Fish1, Fish2),
                                                  names_to = "Useless",
                                                  values_to = "Fish1") %>%
                                    select(-c(Useless)) %>% 
                                    left_join(., smooth_data %>% 
                                    select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))

@@

       add_trace(x = nnd_joined$Fish1_X_Smooth, y = nnd_joined$Fish1_Y_Smooth, z = nnd_joined$Fish1_Z_Smooth,
                 split = nnd_joined$Fish1, type = 'scatter3d', mode = "markers",
                 color = nnd_joined$Fish1,
                 colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%

@@

@@

"2021_7_7_19"  "2021_7_7_27"  "2021_10_8_27" "2021_7_7_16"  "2021_7_7_17"  "2021_7_7_14"  "2021_10_8_21" "2021_10_8_26" "2021_7_7_6"   "2021_10_8_15"

@@

example_data_spline <- comp_data_all %>% filter(Data_ID == "2021_10_8_21")

>>>>

This is to make sure that it's the smae size after I do supsmu

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}
ang_mean <- function(x){rad2deg(atan2(mean(sin(deg2rad(x))),mean(cos(deg2rad(x)))))}

@@

nnd_frame <- 300

@@

select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
                                          filter(Frame_Num %in% c(100, 200, 300)) %>% 
                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
                                          group_by(Fish1, Frame_Num) %>%
                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))

nnd_joined <- example_data %>% select(c(Fish1,Fish2,Frame_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y)) %>%
                                    group_by(Fish1,Frame_Num) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance < 1.9 | all_nas) %>%
                                    mutate(row_n = row_number(),
                                           remove = ifelse(row_n > 1 & is.na(Distance),"Y","N")) %>%
                                    filter(remove == "N") %>%
                                    ungroup() %>%
                                    filter(Frame_Num %in% c(nnd_frame)) %>% 
                                    mutate(Grouping = paste(Frame_Num, Fish1, Fish2)) %>% 
                                    select(c(Frame_Num, Fish1, Fish2, Grouping)) %>%
                                    pivot_longer(c(Fish1, Fish2),
                                                  names_to = "Useless",
                                                  values_to = "Fish1") %>%
                                    select(-c(Useless)) %>% 
                                    #rbind(., individual5_tib) %>%
                                    left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth))

@@

       add_trace(x = select_frames_labeled$Fish1_X_Smooth, y = select_frames_labeled$Fish1_Y_Smooth, z = select_frames_labeled$Fish1_Z_Smooth,
                 split = select_frames_labeled$Fish1, type = 'scatter3d', mode = "markers",
                 color = select_frames_labeled$Fish1,
                 colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%

@@

#make colors the same-ish for groups
#do 2 3d figures and NND figure
```

@@

"2021_7\_7_19" "2021_7\_7_27" "2021_10_8\_27" "2021_7\_7_16" "2021_7\_7_17" "2021_7\_7_14" "2021_10_8\_21" "2021_10_8\_26" "2021_7\_7_6" "2021_10_8\_15"

@@

example_data_spline <- comp_data_all %>% filter(Data_ID == "2021_10_8_27")
